What's in a name? On the automated topic naming of software maintenance activities

### 2010-03-06 icpc/icpc2010.tex
effectiveness
qualties
threats to validity

\subsection{Annotation Observations}

@@

\subsection{Threats to validity}
\textbf{Construct validity} -- Focus on code commit messages, rather than mail or bug trackers. Choice of taxonomy

@@

\textbf{External validity} -- Our data originated from open-source projects in the database domain. Of these, the open-source nature of the project seems most problematic for external validity. However, both projects are developed by commercial entities. Our technique is dependent on development practises including meaningful commit messages, which might not be true in other domains.

@@

% Part of our effort with this project is to understand the qualitative and intentional aspects of requirements in software evolution, a notion we first discussed in \cite{ernst07icsm}. That idea is derived from, in part, work on narratives of software systems shown in academic work from Ant\'{o}n et al.~\cite{anton01}, or more general-purpose work from Waldo~\cite{waldo93}.

@@

% Not sure how do handle this
The idea of extracting higher-level `concerns' (also known as `concepts', `aspects' or `requirements') has been attacked in two ways.

@@

The other approach is to start with code repositories, and try to extract concerns from there. Marcus et al.~\cite{marcus04wcre} describe their use of Latent Semantic Indexing to identify commonly occurring concerns for software maintenance. Some results were interesting, but their precision was quite low. ConcernLines~\cite{treude09cl} shows tag occurrence using colour intensity. They mined change request tags (such as `milestone 3') and used these to make evolutionary analyses of a single product. The presence of a well-maintained set of tags is obviously essential to the success of this technique.
\begin{comment}
%We maintain that these results require more substantive manipulation before being reported to, for example, management. Like any large-scale data analysis project, it requires skill to derive the implications. Hooking the backend results directly to a reporting tool is unlikely to produce useful results.

@@

% comment out or not
% Massey~\cite{massey02icse} and Scacchi~\cite{scacchi02,scacchi05b} looked at the topic of requirements in open-source software. Their work discusses the source of the requirements and how they are used in the development process. German~\cite{german03gnome} looked at GNOME specifically, and listed several sources for requirements: leader interest, mimicry, brainstorming, and prototypes. None of this work  addressed quality requirements in OSS, nor did it examine requirements trends.

% Hindle et al. \cite{Hindle2007} examined release patterns in OSS. They showed that there is a difference between projects regarding maintenance techniques. This supports our result that software qualities are not discussed with the same frequency across projects.

@@

% No we didn't!
% In this paper we showed that a domain specific wordnet for software % development provides better accuracy for labelling topic models than % unsupervised approaches.
%

%* Demonstrated that domain specific knowledge is valuable
%* Demonstrated the feasibility of static approaches and supervised %approaches
%* Showed that non functional requirement pervade much many of the %topics that are extracted

>>>>

\subsection{Annotation observations}

@@

\subsection{Threats to validity}

\begin{comment}
\textbf{Construct validity} -- Focus on code commit messages, rather than mail or bug trackers. Choice of taxonomy

@@

\textbf{External validity} -- Our data originated from open-source projects in the database domain. Of these, the open-source nature of the project seems most problematic for external validity. However, both projects are developed by commercial entities. Our technique is dependent on development practises including meaningful commit messages, which might not be true in other domains.
\end{comment}

Our study suffers from multiple threats to validity. \emph{Construct validity} issues include that used only commit messages rather than mail or bug tracker messages, as well we chose our taxonomy and the data to study. \emph{Internal validity} issues are to do with inter-rater reliability. \emph{External validity} issues are that our data originated from OSS database projects and thus might not be applicable to commercially developed software, as well our analysis techniques relies on a project's commitment to meaningful commit messages.

@@

\begin{comment}
% Part of our effort with this project is to understand the qualitative and intentional aspects of requirements in software evolution, a notion we first discussed in \cite{ernst07icsm}. That idea is derived from, in part, work on narratives of software systems shown in academic work from Ant\'{o}n et al.~\cite{anton01}, or more general-purpose work from Waldo~\cite{waldo93}.

@@

% Not sure how do handle this
\end{comment}
The idea of extracting higher-level `concerns' (also known as `concepts', `aspects' or `requirements') has been attacked in two ways.

@@

The other approach is to start with code repositories, and try to extract concerns from there. Marcus et al.~\cite{marcus04wcre} describe their use of Latent Semantic Indexing to identify commonly occurring concerns for software maintenance. Some results were interesting, but their precision was quite low. ConcernLines~\cite{treude09cl} shows tag occurrence using colour intensity. They mined change request tags (such as `milestone 3') and used these to make evolutionary analyses of a single product. The presence of a well-maintained set of tags is obviously essential to the success of this technique.

\begin{comment}
%We maintain that these results require more substantive manipulation before being reported to, for example, management. Like any large-scale data analysis project, it requires skill to derive the implications. Hooking the backend results directly to a reporting tool is unlikely to produce useful results.

@@

\begin{comment}
% comment out or not
% Massey~\cite{massey02icse} and Scacchi~\cite{scacchi02,scacchi05b} looked at the topic of requirements in open-source software. Their work discusses the source of the requirements and how they are used in the development process. German~\cite{german03gnome} looked at GNOME specifically, and listed several sources for requirements: leader interest, mimicry, brainstorming, and prototypes. None of this work  addressed quality requirements in OSS, nor did it examine requirements trends.

% Hindle et al. \cite{Hindle2007} examined release patterns in OSS. They showed that there is a difference between projects regarding maintenance techniques. This supports our result that software qualities are not discussed with the same frequency across projects.
\end{comment}

@@
